A mixture of hidden Markov models to predict the lymphatic spread in head and neck cancer

### 2024-01-19 content/manuscript.qmd
update data, add preval plot, and add it to text

>>>>

![Prevalence of LNL involvement stratified by subsite. The subsites are sorted in ascending order by their prevalence of involvement in LNL II. Oral cavity subsites are plotted in shaed of blue, oropharynx subsites in shades of orange.](../figures/prevalence_by_subsite.svg){#fig-prevalence-by-subsite fig-pos="b" width="49%"}
